\propertitle

### 2019-11-20 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-20T17:26:55+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

@@

Before applying the formula above to two concrete data sets we want to add
two remarks about the maximum-entropy method that are seldom made in the
neuroscientific literature. They are important for the interpretation of
the results and are further discussed in \sect~\ref{sec:assumptions}.

First, the distribution $\px(\yA \| M, N)$ given by this method is the
zeroth-order approximation (in the sense of Laplace's
method)\citep[\chap~4]{debruijn1958_r1961}{tierneyetal1986,strawderman2000}
of four different distributions for the full network, which differ
numerically from one another in higher-order approximations:
\begin{enumerate}[label=(\roman*)]
\item the most probable \emph{frequency} distribution for the total
  activity across the \emph{recorded} bins, %$\yFF(\yA)$,
\item the \emph{belief} distribution for the value of the total
  activity at any time bin among those \emph{recorded},
  %$\yp(\yA_{t} \| \yH)$ with $1\le t \le T$,
\item the most probable \emph{frequency} distribution for the total
  activity in a very long run of \emph{new} time bins, %$\ynuu(\yA)$,
\item the \emph{belief} distribution for the value of the total
  activity at a \emph{new} time bin.
  % $\yp(\yA_{t} \| \yH)$ with $t<1$ or $t>T$
\end{enumerate}

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-20T20:23:20+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The number and degrees of the constraining moments depend on the questions
and hypotheses that a researcher is exploring; for example, hypotheses
about the \enquote{cooperativity} or \enquote{interaction} in the network
activity. We discuss this kind of use in \sect~\ref{sec:marginalization}.
Note that the constraint equation~\eqref{eq:final_constraint} for the
distribution~\eqref{eq:app_maxent_pop_first} \emph{may not have exact
  solutions} if $N$ is strictly larger than $n$; and the possible
discrepancy increases with the number of constraints. The essential reason
for this discrepancy is the approximate character of two assumptions on
which the maximum-entropy method is based and of one assumption specific to
our application: measured moments equal expectations (or equivalently that
the number of time bins $T$ is infinite), the order of the time bins is
irrelevant, and that all full-network subsets with $\yA$ neurons are
equally likely to be generating a total activity $\yA$. We discuss these
assumptions in \sect~\ref{sec:assumptions}.

%, but our main goal is to simply introduce
% the general method without entering into biological questions of this
% kind.

@@

Before applying the formula above to two concrete data sets we want to add
three remarks on the maximum-entropy method that are seldom made in the
neuroscientific literature. They are important for the interpretation of
the results and are further discussed in \sect~\ref{sec:assumptions}.

First, a maximum-entropy distribution, like $\px(\yA \| M, N)$, is the
zeroth-order approximation (in the sense of Laplace's
approximation)\citep[\chap~4]{debruijn1958_r1961}{tierneyetal1986,strawderman2000}
of four different distributions for the full network, which differ
numerically from one another in higher-order approximations:
\begin{enumerate}[label=(\roman*)]
\item the most probable \emph{frequency} distribution for the total
  activity across the \emph{recorded} bins, %$\yFF(\yA)$,
\item the \emph{belief} distribution for the value of the total
  activity at any time bin among those \emph{recorded},
  %$\yp(\yA_{t} \| \yH)$ with $1\le t \le T$,
\item the most probable \emph{frequency} distribution for the total
  activity in a very long run of \emph{new} time bins, %$\ynuu(\yA)$,
\item the \emph{belief} distribution for the value of the total
  activity at a \emph{new} time bin.
  % $\yp(\yA_{t} \| \yH)$ with $t<1$ or $t>T$
\end{enumerate}
